SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization

### 2014-06-17 paper/paper.tex
paper: Added Regehr citation.

HDD is most similar to SmartCheck's reduction algorithm, with an important
difference: HDD (and DD) is deterministic, so the algorithm only succeeds in
reducing the counterexample only if a new counterexample can be constructed from
the original one.  Our approach combines the speed of delta debugging with the
power of QuickCheck to \emph{randomly} discover structurally smaller
counterexamples; in short, this is the first treatment we know of that
integrates counterexample generation with counterexample reduction.
Furthermore, neither paper explores the idea of counterexample generalization.

>>>>

HDD is most similar to SmartCheck's reduction algorithm, with an important
difference: HDD (and DD) is deterministic, so the algorithm only succeeds in
reducing the counterexample only if a new counterexample can be constructed from
the original one.  Our approach combines the speed of delta debugging with the
power of QuickCheck to \emph{randomly} discover structurally smaller
counterexamples.  The idea of randomization in test-case reduction was developed
at approximately the same time as SmartCheck and first reported in the domain of
reducing C~programs that demonstrate compiler bugs~\cite{regehr}.  We believe our
work is the first to explore the technique in a more general setting.
Furthermore, we believe ours is the first to explore the idea of counterexample
generalization.
